---
title: "Instructions for COLM 2026 Submissions"

author:
  - name: "Alice Smith"
    affiliations:
      - name: "University of Nowhere"
    email: alice.smith@nowhere.edu
  - name: "Bob Jones"
    affiliations:
      - name: "Institute of Made-Up Science"
    email: bob.jones@madeup.edu

abstract: |
  This document contains instructions for preparing a submission to
  COLM 2026 using the **colm** Quarto template. It also serves as a
  demonstration of the template's formatting: the document you are
  reading is itself typeset using the template. Replace the YAML fields
  above and the section content below with your own manuscript.

bibliography: example.bib

colm-mode: submission   # submission | preprint | final

tbl-cap-location: bottom

format:
  colm-pdf: default
---

# Installation

The easiest way to install this template is directly from GitHub.
Run the following command from your project directory:

```{=latex}
\begin{verbatim}
quarto add znhoughton/quarto-templates/colm
\end{verbatim}
```

Alternatively, if you have a local clone of the repository, you can
install from the local path instead:

```{=latex}
\begin{verbatim}
quarto add "path/to/quarto-templates/colm"
\end{verbatim}
```

Either method copies the `_extensions/colm/` folder into your project.
Once installed, set the format in your document's YAML front matter:

```{=latex}
\begin{verbatim}
format:
  colm-pdf: default
\end{verbatim}
```

Then render with:

```{=latex}
\begin{verbatim}
quarto render your-document.qmd
\end{verbatim}
```

The extension folder is self-contained and can be committed to your
repository so that collaborators do not need a separate installation
step. The `_extensions/` folder should not be listed in `.gitignore` if
you want the template to be available to everyone who clones the
repository. To update the template to the latest version at any time,
simply re-run the `quarto add` command from above.

# Text Formatting

This document is typeset using the `colm` template. The body text you
are reading demonstrates the default Palatino font (tgpagella +
mathpazo) and two-column layout. Inline formatting options include
**bold**, *italic*, `inline code`, and [small caps]{.smallcaps}.

Long tables and figures can span both columns using the `table*` and
`figure*` LaTeX environments in a raw LaTeX block. Paragraphs are
separated by a blank line. A single line break within a paragraph does
not produce a new paragraph.

The COLM template uses Palatino for body text and Inconsolata for
monospace. Font size, line spacing, and margins are set by the bundled
class file and should not be overridden. Do not add custom geometry,
font, or spacing commands to your document.

Section headings use `#` for top-level sections and `##` for
subsections. The template numbers sections automatically; do not add
manual numbering to heading text [@Smith2020].

# Tables

Use an R chunk with `knitr::kable()` and the `#| label:` and
`#| tbl-cap:` chunk options to produce tables.

```{r}
#| label: tbl-example
#| tbl-cap: "A simple table showing condition means."
#| echo: false
knitr::kable(
  data.frame(Condition = c("A", "B"), Mean = c(1.2, 2.4), SD = c(0.3, 0.5)),
  format = "latex", align = c("l", "r", "r"), booktabs = TRUE
)
```

Cross-reference with `@tbl-example`, which produces @tbl-example.
Tables that span both columns use a `table*` environment in a raw
LaTeX block. Keep single-column tables narrow enough to fit within
one column width; use the `table*` environment only when the content
genuinely requires the full page width.

# Figures

Use an R chunk with `#| label: fig-xxx` and `#| fig-cap:` chunk
options to produce figures with captions and cross-reference labels.

```{r}
#| label: fig-example
#| fig-cap: "A simple scatter plot for illustration."
#| echo: false
plot(1:5, c(2.1, 3.4, 2.8, 4.2, 3.9),
     xlab = "Condition", ylab = "Mean RT (s)", pch = 19)
```

Cross-reference with `@fig-example`, which produces @fig-example.
Wide figures can span both columns using a `figure*` environment in a
raw LaTeX block. Figures are floating by default and will be placed at
the top or bottom of the nearest page. For publication-quality plots,
prefer vector formats (PDF or SVG) over raster formats (PNG, JPEG)
to ensure sharpness at any print resolution.

# Equations

Inline math: $y = \beta_0 + \beta_1 x + \varepsilon$.

Display equation:

$$
Y_{ij} = \beta_0 + \beta_1 X_{ij} + u_i + \varepsilon_{ij}
$$ {#eq-model}

Cross-reference with `@eq-model`, which produces @eq-model.

Multi-line display equations:

$$
\mu_i = \alpha + \beta x_i, \quad y_i \sim \mathcal{N}(\mu_i, \sigma^2)
$$

Use display equations for any expression that is important enough to
be referred to by number. Number only equations that are actually
cross-referenced in the text; unnumbered display equations use the
plain `$$...$$` syntax without a label.

The `amsmath` package is loaded by the template and provides
environments such as `align`, `gather`, and `cases` via raw LaTeX
blocks. Inline math uses standard `$...$` delimiters. Avoid mixing
LaTeX math commands with Pandoc markdown constructs in the same
expression.

# Submission Modes

Change `colm-mode` in the YAML front matter to switch modes:

```{r}
#| label: tbl-modes
#| tbl-cap: "COLM submission modes."
#| echo: false
knitr::kable(
  data.frame(
    Mode       = c("submission", "preprint", "final"),
    Authors    = c("anonymous", "shown", "shown"),
    Lines      = c("yes", "no", "no"),
    Header     = c("(none)", "Preprint. Under review.", "Published at COLM 2026")
  ),
  format = "latex", align = c("l", "l", "l", "l"), booktabs = TRUE
)
```

In `submission` mode the document is anonymised and line numbers are
added for reviewer reference. The author list is suppressed. In
`final` mode, authors and affiliations are shown and line numbers are
removed. Use `preprint` for posting to arXiv or a personal website
before the camera-ready deadline. Switch modes by changing a single
YAML field; no other changes to the document are needed.

Remember to remove or anonymise any self-identifying references in the
manuscript body before submitting in `submission` mode. This includes
references to your own prior work that would reveal authorship, links
to personal repositories, and acknowledgements. Restore these for the
`final` camera-ready version.
