---
title: "Instructions for ACL Proceedings"

author:
  - name: "Alice Smith"
    affiliations:
      - name: "University of Nowhere"
    email: alice.smith@nowhere.edu
  - name: "Bob Jones"
    affiliations:
      - name: "Institute of Made-Up Science"
    email: bob.jones@madeup.edu

abstract: |
  This document contains instructions for preparing a submission to ACL
  and affiliated venues using the **acl** Quarto template. It also serves
  as a demonstration of the template's formatting: the document you are
  reading is itself typeset using the template. Replace the YAML fields
  above and the section content below with your own manuscript.

bibliography: example.bib

acl-mode: review   # review | final | preprint

tbl-cap-location: bottom

format:
  acl-pdf:
    keep-tex: true
---

# Installation

The easiest way to install this template is directly from GitHub.
Run the following command from your project directory:

```{=latex}
\begin{verbatim}
quarto add znhoughton/quarto-templates/acl
\end{verbatim}
```

Alternatively, if you have a local clone of the repository, you can
install from the local path instead:

```{=latex}
\begin{verbatim}
quarto add "path/to/quarto-templates/acl"
\end{verbatim}
```

Either method copies the `_extensions/acl/` folder into your project.
Once installed, set the format in your document's YAML front matter:

```{=latex}
\begin{verbatim}
format:
  acl-pdf: default
\end{verbatim}
```

Then render with:

```{=latex}
\begin{verbatim}
quarto render your-document.qmd
\end{verbatim}
```

The extension folder is self-contained and can be committed to your
repository so that collaborators do not need a separate installation
step. The `_extensions/` folder should not be listed in `.gitignore` if
you want the template to be available to everyone who clones the
repository. To update the template to the latest version at any time,
simply re-run the `quarto add` command from above.

# Text Formatting

This document is typeset using the `acl` template. The body text you
are reading demonstrates the default two-column layout, font, and
spacing. Inline formatting options include **bold**, *italic*,
`inline code`, and [small caps]{.smallcaps}.

Long tables and figures can span both columns using the `table*` and
`figure*` LaTeX environments in a raw LaTeX block. Paragraphs are
separated by a blank line. A single line break within a paragraph does
not produce a new paragraph.

The ACL template uses Times Roman for the body text and Helvetica for
line numbers. Font size is 11pt with two-column layout. Line spacing
and margins are set by `acl.sty` and should not be overridden. Do not
add custom geometry, font, or spacing commands to your document.

Section headings use `#` for top-level sections and `##` for
subsections. ACL papers do not typically use headings deeper than
`###`. The template numbers sections automatically; do not add manual
numbering to heading text [@Smith2020].

# Tables

Use an R chunk with `knitr::kable()` and the `#| label:` and
`#| tbl-cap:` chunk options to produce tables.

```{r}
#| label: tbl-example
#| tbl-cap: "A simple table showing condition means."
#| echo: false
knitr::kable(
  data.frame(Condition = c("A", "B"), Mean = c(1.2, 2.4), SD = c(0.3, 0.5)),
  format = "latex", align = c("l", "r", "r"), booktabs = TRUE
)
```

Cross-reference with `@tbl-example`, which produces @tbl-example.
Tables that span both columns use a `table*` environment in a raw
LaTeX block. Keep single-column tables narrow enough to fit within
one column width; use the `table*` environment only when the content
genuinely requires the full page width.

# Figures

Use an R chunk with `#| label: fig-xxx` and `#| fig-cap:` chunk
options to produce figures with captions and cross-reference labels.

```{r}
#| label: fig-example
#| fig-cap: "A simple scatter plot for illustration."
#| echo: false
plot(1:5, c(2.1, 3.4, 2.8, 4.2, 3.9),
     xlab = "Condition", ylab = "Mean RT (s)", pch = 19)
```

Cross-reference with `@fig-example`, which produces @fig-example.
Wide figures can span both columns using a `figure*` environment in a
raw LaTeX block. Figures are floating by default and will be placed at
the top or bottom of the nearest page. For publication-quality plots,
prefer vector formats (PDF or SVG) over raster formats (PNG, JPEG)
to ensure sharpness at any print resolution.

# Equations

Inline math: $y = \beta_0 + \beta_1 x + \varepsilon$.

Display equation:

$$
Y_{ij} = \beta_0 + \beta_1 X_{ij} + u_i + \varepsilon_{ij}
$$ {#eq-model}

Cross-reference with `@eq-model`, which produces @eq-model.

Multi-line display equations:

$$
\mu_i = \alpha + \beta x_i, \quad y_i \sim \mathcal{N}(\mu_i, \sigma^2)
$$

Use display equations for any expression that is important enough to
be referred to by number. Number only equations that are actually
cross-referenced in the text; unnumbered display equations use the
plain `$$...$$` syntax without a label.

The `amsmath` package is loaded by the template and provides
environments such as `align`, `gather`, and `cases` via raw LaTeX
blocks. Inline math uses standard `$...$` delimiters. Avoid mixing
LaTeX math commands with Pandoc markdown constructs in the same
expression.

# Submission Modes

Change `acl-mode` in the YAML front matter to switch modes:

```{r}
#| label: tbl-modes
#| tbl-cap: "ACL submission modes."
#| echo: false
knitr::kable(
  data.frame(
    Mode    = c("review", "final", "preprint"),
    Authors = c("anonymous", "shown", "shown"),
    Lines   = c("yes", "no", "no"),
    Use     = c("submission", "camera-ready", "arXiv")
  ),
  format = "latex", align = c("l", "l", "l", "l"), booktabs = TRUE
)
```

In `review` mode the document is anonymised and line numbers are added
for reviewer reference. The author list is replaced with "Anonymous ACL
submission." In `final` mode, authors and affiliations are shown and
line numbers are removed. Use `preprint` for posting to arXiv or a
personal website before the camera-ready deadline. Switch modes by
changing a single YAML field; no other changes to the document are
needed.

Remember to remove or anonymise any self-identifying references in the
manuscript body before submitting in `review` mode. This includes
references to your own prior work that would reveal authorship, links
to personal repositories, and acknowledgements. Restore these for the
`final` camera-ready version.
